Crowdsourced geometric morphometrics enable rapid large-scale collection and

### 2015-04-29 manuscript/manuscript.Rmd
Fix up figures

---
title: Crowdsourced geometric morphometrics enable rapid large-scale collection and
  analysis of phenotypic data
author:
- affiliation: ucla
  email: jonathan.chang\@ucla.edu
  footnote: Author for correspondence jonathan.chang\@ucla.edu
  name: Jonathan Chang
- affiliation: ucla
  name: Michael E. Alfaro
bibliography:
- library.bib
- knitcitations.bib
output:
  pdf_document:
    fig_caption: yes
    keep_tex: yes
    latex_engine: xelatex
    template: inc/mstemplate.tex
  html_document:
    toc: yes
  word_document: default
documentclass: inc/msarticle
fontsize: 11pt
geometry: margin=1.2in
layout: preprint
lineno: yes
linestretch: 1.05
csl: inc/methods-in-ecology-and-evolution.csl
running_head: Fast crowdsourced phenotypic data collection
address:
- address: |
    Department of Ecology and Evolutionary Biology, University of California, Los Angeles, CA, USA
  code: ucla
word_count: 6000?
---

```{r prelude, echo=FALSE, message=FALSE, warning=FALSE}
library("MASS")
library("readr")
library("dplyr")
library("ggplot2")
library("stringr")
library("magrittr")
library("tidyr")
library("reshape2")
library("scales")
library("grid")
library("geomorph")
library("rjson")
library("ipred")
library("vegan")
library("lubridate")
library("directlabels")
library("BAMMtools")
library("knitcitations")
library("kfigr")
library("fish.reliability")
options("citation_format"="pandoc")
cleanbib()
set.seed(111) # reproducible and stable sampling
data(fish_landmarks)
data(fish_families)
knitr::opts_chunk$set(echo=FALSE, cache=1)
```

@@

```{r turk_morph_procrustes_space, fig.cap="Hello", anchor="figure", message=FALSE}
# Load data from the anonymized results file, remove students, drop bad marks
df <- fish_landmarks %>%
	filter(role != "student") %>% 
	separate(col=mark, into=c("cat", "cat_seq"), sep=1, remove=F, convert=T) %>%
	filter(!(family %in% c("Bal") & mark %in% c("D1","D2")), !mark %in% c("O1","O2","O3","O4","O5", "A3", "D3", "D4"))

@@

```{r bamm_plots, message=F, warning=F, anchor="figure"}
df <- fish_families %>% group_by(tip, mark, family) %>% summarise(x=median(x), y=median(y))

@@

```{r timing_plot, fig.cap="Line plot showing time to receive results for any given image (x axis) and the total fraction of the data set received (y axis). Landmarks were first received `r timing_data[[1, 'time']] %>% dminutes()` after creation of the Amazon MTurk task, and at least one replicate was received for every image at the 80 minute mark."}
# median time (in minutes) it takes an expert to measure these fishes
timings <- (no_st %>% group_by(role) %>% summarise(duration=median(duration))) %>% mutate(total_time=duration * nrow(no_st))

@@

@@

>>>>

---
title: Crowdsourced geometric morphometrics enable rapid large-scale collection and
  analysis of phenotypic data
author:
- affiliation: ucla
  email: jonathan.chang\@ucla.edu
  footnote: Author for correspondence jonathan.chang\@ucla.edu
  name: Jonathan Chang
- affiliation: ucla
  name: Michael E. Alfaro
bibliography:
- library.bib
- knitcitations.bib
output:
  pdf_document:
    fig_caption: yes
    fig_height: 5
    fig_width: 7
    keep_tex: yes
    latex_engine: xelatex
    template: inc/mstemplate.tex
  html_document:
    toc: yes
  word_document: default
documentclass: inc/msarticle
fontsize: 11pt
geometry: margin=1.2in
layout: preprint
lineno: yes
linestretch: 1.05
csl: inc/methods-in-ecology-and-evolution.csl
running_head: Fast crowdsourced phenotypic data collection
address:
- address: |
    Department of Ecology and Evolutionary Biology, University of California, Los Angeles, CA, USA
  code: ucla
word_count: 6000?
---

```{r prelude, echo=FALSE, message=FALSE, warning=FALSE}
library("MASS")
library("readr")
library("dplyr")
library("ggplot2")
library("stringr")
library("magrittr")
library("tidyr")
library("reshape2")
library("scales")
library("grid")
library("geomorph")
library("rjson")
library("ipred")
library("vegan")
library("lubridate")
library("directlabels")
library("BAMMtools")
library("knitr")
library("kfigr")
library("knitcitations")
library("fish.reliability")
options("citation_format"="pandoc")
cleanbib()
set.seed(111) # reproducible and stable sampling
data(fish_landmarks)
data(fish_families)
knitr::opts_chunk$set(echo=FALSE, cache=1, fig.align="center")
```

@@

```{r turk_morph_procrustes_space, fig.cap="Turker morpho space", anchor="figure"}
# Load data from the anonymized results file, remove students, drop bad marks
df <- fish_landmarks %>%
	filter(role != "student") %>% 
	separate(col=mark, into=c("cat", "cat_seq"), sep=1, remove=F, convert=T) %>%
	filter(!(family %in% c("Bal") & mark %in% c("D1","D2")), !mark %in% c("O1","O2","O3","O4","O5", "A3", "D3", "D4"))

@@

```{r bamm_plots, message=F, warning=F, fig.show="hold", fig.cap="Family figures", anchor="figure"}
df <- fish_families %>% group_by(tip, mark, family) %>% summarise(x=median(x), y=median(y))

@@

asdfsdf

```{r timing_plot, fig.cap="Line plot showing time to receive results for any given image (x axis) and the total fraction of the data set received (y axis). Landmarks were first received 8 minutes after creation of the Amazon MTurk task, and at least one replicate was received for every image at the 80 minute mark.", anchor="figure"}
# median time (in minutes) it takes an expert to measure these fishes
timings <- (no_st %>% group_by(role) %>% summarise(duration=median(duration))) %>% mutate(total_time=duration * nrow(no_st))

@@

<!-- reset figure numbering for supplement -->

\renewcommand\thefigure{S\arabic{figure}}
\setcounter{figure}{0}

```{r}
knitr::opts_chunk$set(fig.cur=1)
```

@@

<!-- spit out all figures before references -->
\clearpage
